Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-17 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Reorganizing subsections
Also refs #81. Now it's clearer what has been done.

\subsection{Experimental trials}
\label{sec:w2Exp}

@@

@@

\subsection{Experimental results}

@@

Finally, the implementation needs some refinement in terms of
programming and also ease of use. Tools such as Yeoman might be used % ¿añadir una cita o la URL http://yeoman.io/ a pie de página ?
to create a generator in which the user just has to create a fitness
function, with the rest of the framework wrapped around
automatically. All this, as the data used for this paper and the paper
itself, has been published with a free license in GitHub at
\url{https://github.com/JJ/modeling-volunteer-computing}.

>>>>

\subsection{First experiments}
\label{sec:w2Exp}

@@

\subsection{Tests with floating-point hard optimization problems}

@@

@@

Finally, the implementation needs some refinement in terms of
programming and also ease of use. Tools such as Yeoman might be used % ¿añadir una cita o la URL http://yeoman.io/ a pie de página ?
to create a generator in which the user just has to create a fitness
function, with the rest of the framework wrapped around
automatically. All this, as well as the data used for this paper and the paper
itself, has been published with a free license in GitHub at
\url{https://github.com/JJ/modeling-volunteer-computing}.
